---
title: "COVID19 USA"
author: "Chanho Hyun"
date: '2022 2 15 '
output:
  pdf_document: 
    fig_width: 10
  word_document: default
  html_document:
    df_print: paged
---

I used USA COVID19 data until 2020 Dec 10th. 

I did not consider about the new variation of COVID19 such as "Omicron" so my result might be inaccurate.

Goal: Find out the relationship between the ratio of white people in each
state and cases_per_100,000. (Dose white ratio affects the cases of
COVID19?)

Sub Goal: If white ratio and cases_per_100,000 has no relationship, then
find out the relationship between other variables.


```{r}
df <- data.frame("variable" = c("state", "white_ratio", "cases per 100,000",
                                "ses", "sex", "oler than 65"), "Description" 
                 = c("name of states", "white ratio", "cases per 100,000", 
                     "socioeconomic status of the people", 
" if the state has more male population than female population, 1, otherwise 0",
"ratio of people who are older than 65"))
df
```




This is the table represents my variables. 
I could not get each person data who is within a state, but if there is the data about each person, then I would expect that people in the same state are not independent of each other. There is likely a region effect that would violate independence assumption. 
However, for this project I could not get the individual's data of each state, 
so we can skip this violation. (I cannot use LMM for this project)

*ses is median_household_income*




```{r}
library(readr)
library(ggplot2)
library(tidyverse)


state <- read_csv("state.csv")
ggplot(data=state, aes(x=cases_per, y=white_ratio)) + 
  geom_point(alpha = 0.5) + geom_smooth(method = "lm", se = FALSE) + 
  theme_classic()
```




This a scatter plot to examine the relationship between casese per
100,000 and white_ratio Include a line of best fit. 

Followed by scatter plot, line of best fit shows there is a reasonable relationship between cases_per_100,000 and minotirty_status since it has positive slope. 
However, if there is no line of best fit, it is hard to find out the relationship between white_ratio and cases_per because dots are too scattered.




```{r}
lm <- lm(white_ratio ~ cases_per + sex + median_household_income + 
           older_than_65, data = state)

summary(lm)
```




This is linear model with test as the response and use cases_per_100,000, sex, median_household_income, ratio of people who are older than 65 as the covariates.Followed by p-value, cases_per, median_household_income, and older_than_65 are statistically significant, but sex is not.




```{r}
confint(lm)
```




Followed by confint(lm), my (intercept) which is 95% confidence interval
of white ratio has negative lower bound. So, I put zero instead of
negative lower- bound. Thus, we can claim that with 95% conficence, our
intercept is between 0 and 1.7028e+00.

cases_per looks statistically significant. With 95% of confidence, one
unit increase in cases_per, white_ratio is changed from 1.6998e-03 to
4.5766e-03

As a result, we can confirm that cases_per and white_ratio do have
relationship. However, we got negative lower bound for our 95%
confidence of intercept and the differences between cases_per's lower
bound and upper bound is too small. Therefore, we cannot claim that the
ratio of white people affects cases_per.

I wanted to use linear mixed model function for my project, but I could
not get the data from each person in each state, so I could not use lmm
for this project.



citation:

Covid-19 in the United States. Data USA. (n.d.). Retrieved February 15, 2022,
from https://datausa.io/coronavirus 

U.S. Census Bureau quickfacts: California. (n.d.). Retrieved February 15, 2022, 
from https://www.census.gov/quickfacts/fact/table/CA/PST045221 
